---
title: "Factors Affecting the Salary of an employee"
output: html_document
date: '2022-06-05'
--- 




```{r}
#Reading the dataset
data = read.csv('project data.csv')

data
```

```{r}
#Structure of Dataset
str(data)
```
We have 1470 rows and   35 columns in our Dataset:




```{r}
#Checking for null values in the numerical columns.
library(DataExplorer)
library(dplyr)
plot_missing(data)
```
We dont have any null Values in the dataset.


```{r}
#let's remove unnecessary columns 
table(data$StandardHours)
table(data$EmployeeCount)
table(data$Over18)

data = subset(data, select = -c(EmployeeCount,StandardHours,Over18) )
```



```{r}

data_num = select_if(data,is.numeric)
data_num
```

#Lets look at the Correlation between the variables in the Given Dataset :

```{r}
library(corrplot)
corrplot(cor(data_num), is.corr = FALSE, method = "square")
```
This is hard to interpret the highly correlated values with Salary Variable,
so let's look deep into the salary variable

```{r}
library(lares)
corr_var(data_num, 
  MonthlyIncome,
  top = 5 # display top 5 correlations
)
```
The Top 5 Factors of a persons Monthly Income  are Joblevel ,TotalWorkingYears,YearsAtCompany, Age, YearsIncurentRole



```{r}
#Modelling

model = lm(MonthlyIncome ~. ,data = data)
summary(model)

```

Our Model is able to understand the  0.9449 (94.49%) of deviance in the Data

The Variables JobLevel,TotalWorkingYears,JobRoleLaboratory Technician ,JobRoleManager ,JobRoleResearch Director,JobRoleResearch Scientist      are highly significant in predicting the monthly Salary of a person followed by the variables 
YearsSinceLastPromotion ,YearsWithCurrManager  ,JobInvolvement.